### 2019-12-06 article.tex
bayesian deep learning section added

%\usepackage[authoryear,longnamesfirst]{natbib}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
%\usepackage{mathpazo}

@@

>>>>

%\usepackage[authoryear,longnamesfirst]{natbib}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
\usepackage{amsmath}
%\usepackage{mathpazo}

@@

Let $\hat{y}$ be the output of a NN model with $L$ layers and a loss function {\it E(·, ·)} such as the softmax loss or the Euclidean loss (square loss).We denote by $W_i$ the NN’s weight matrices of dimensions $K_i \times K_{i-1}$, and by $b_i$ the bias vectors of dimensions $K_i$ for each layer $i = 1, ..., L$. We denote by $y_i$ the observed output corresponding to input $x_i$ for $1 \leq i \leq N$ data points, and the input and output sets as $X, Y$. During NN optimization a regularization term is often added. We often use $L2$ regularization weighted by some weight decay $\lambda$, resulting in a minimization objective (often referred to as cost) and it can written as Equation  \eqref{eq:bayesianCnnDroupout} \cite{Gal2016}.

\begin{equation}
\mathcal{L}_{dropout} := 
    {1 \over N} \sum_{i=1}^{N} E(y_i , \hat{y_i}) + \\
    \lambda \sum_{i=1}^{L} ( \left|\left| W_i \right|\right|_2^2 + \left|\left| b_i \right|\right|_2^2 )
\label{eq:bayesianCnnDroupout} 
\end{equation}

Now of if we add dropout to the calculations each unit may remain the same with probability $p_i$ or dropped out (its value is set to zero). We use the same values in the backward pass propagating the derivatives to the parameters. Assume we are given a covariance function of the form of Equation \eqref{eq:nnCovariance}.

\begin{equation}
K(x, y) = \int p(w)p(b) \sigma (w^T x + b) \sigma (w^T y + b) dw db
\label{eq:nnCovariance}
\end{equation}

with some element-wise non-linearity {\it $\sigma$(·)} and distributions $p(w), p(b)$. It had been shown that a deep Gaussian process with L layers and covariance function $K(x,y)$ can be approximated by placing a variational distribution over each component of a spectral decomposition of the GPs’ covariance functions.

Let $W_i$ be a random matrix of dimensions $K \times K_{i-1}$ for each layer $i$, and write
$\omega = \{ W_i \}^L_{i=1}$. A priori,we let each row of $W_i$ distribute according to the $p(W)$ above. In addition, assume vectors $m_i$ of dimensions $K_i$ for each GP layer. The predictive probability of the deep GP model given some precision parameter $\tau > 0$ can be parameterized as Equation \eqref{eq:gpPriority}.

\begin{eqnarray}
\label{eq:gpPriority}
p(y | x,X,Y) = \int p(y|x,\omega) p(\omega|X,Y)d\omega \\ 
p(y|x,\omega) = \mathcal{N} (y ; \hat{y} (x,\omega) , \tau^{-1} I_D )  \nonumber \\
\hat{y} (x, \omega = \{ W_1, ..., W_L \}) =  \nonumber \\
\sqrt{1 \over K_L} W_L \sigma( ...  \sqrt{1 \over K_1} W_2 \sigma( W_1 x + m_1 ) ... )  \nonumber
\end{eqnarray}

The posterior distribution $p(\omega|X,Y)$ in Equation \eqref{eq:gpPriority} is intractable. It had been shown that if we use a distribution over matrices whose columns are randomly set to zero, we can recover Equation \eqref{eq:bayesianCnnDroupout} \cite{Gal2016}. Note that previously mentioned distribution $q(\omega)$ can be defined as:

\begin{eqnarray}
W_i &=& M_i \cdot diag([ z_{i,j} ]^{K_i}_{j=1} ) \nonumber \\ 
z_{i,j} &=& Bernoulli(p_i) \; \forall \; 1 \le i \le L \; , \; 1 \le j \le K_{i-1} \nonumber
\end{eqnarray}
\newline
given some probabilities $p_i$ and matrices $M_i$ as variational parameters. The variable $z_{i,j} = 0$ corresponds then to unit $j$ in layer $i-1$ being dropped out as an input to layer $i$. Subsequently if we use a dropout in 3D convolutional neural network, it would be a practice of Bayesian 3D CNN.
